---
title: "EPOC development"
author: "Andrew Constable"
date: "14/11/2021"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("EPOC")
```

# Scenario: Test

## To do
  
1. Check to see whether NetCDF files can be appended without adding much overhead  
1. Use NetCDF rather than flat files for  
    i. environment data  
    i. printing State of environment (thus have variable names with files)  
  
  
## Description

*Test* implements a new Universe based on a simple spatial domain (1 area), scenario (3 replicate time series), and a single environmental variable.  
  
The environmental variable has a stochastic component.  Rather than calling the random number generator at each time step, the variable is saved to file, allowing for statistical analysis as well as re-use under many circumstances. The following steps occur:  
  
1. During setup, if the file is not present then it is created according to the specifications  
1. Runtime - reads one line of the file per time step to update the state of the environment, and prints the state at that time.  
  
This simple example illustrates how EPOC works, including the need for *code* and *data* files.  
  
Although names can be self-determined, three essential input data scripts are:  
  
* Universe - the file name is used in the function call epoc().  The default is 'Universe.data.R'  
* Spatial configuration (polygons) - the filename is detailed in the Universe data script.  
* Scenario details - the filename is detailed in the Universe data script.  

## Runtime and Analysis

```{r , include=FALSE, echo=FALSE}
source("sTest_install_catalogue.R")
epoc()
````

